COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-05-04 paper.Rmd
update files

- name: Julio S. Solís Arce, BA^[First author]

@@

  affiliation: International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)

@@

  affiliation: Economics Department of Ghent University

@@

- name: Dean Karlan, PhD^[Last author]

@@

@@

```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}

>>>>

- name: Julio S. Solís Arce, BA^[First author.]

@@

  affiliation: International Center for the Study of Institutions and Development, HSE University

@@

  affiliation: Department of Economics, Ghent University

@@

- name: Dean Karlan, PhD^[Last author.]

@@

#  - \usepackage{lineno}
#  - \linenumbers

@@

```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}
knitr::opts_chunk$set(echo = FALSE)
```
